SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-11-16 design.tex
Incorporating suggestions

\section{SPP-Perc}

\subsection{Changes made to original SPP}
To modify the SPP Design to suit our scheme, the following changes were made:

\begin{itemize}
\item \textbf{Original Thresholds discarded}\newline In the original
  SPP design, an internal confidence mechanism was developed which was
  compared against a preset PF\_THRESHOLD (T\textsubscript{p}) to
  decide whether to accept or reject the prefetch suggestion.
  Furthermore, the accepted suggestions were thresholded against FILL
  \_THRESHOLD (T\textsubscript{f}) to decide the fill level: L2 Cache
  vs Last Level Cache.  T\textsubscript{p} and T\textsubscript{f} were
  set to 25 and 90 respectively, on the scale of 0 to 100.  In
  SPP-Perc, the perceptron sum is used to make these decisions.  Hence
  these two thresholds are no longer needed

\item \textbf{Looking at L2 MSHR Queue while prefetching}\newline
  Original SPP would not consider the slots available in the L2 MSHR
  queue.  It had an assumption that at no time can the number of
  prefetches suggested by SPP could exceed the capacity of the queue.
  While it was not proven in the paper, the internal confidence
  mechanism along with the thresholds made sure that the above
  assumption was maintained.  In SPP-Perc since there can be no
  assumption on the degree of aggressiveness - because SPP is being
  tuned to its lowest thresholds, we explicitly check that at no point
  should the number of suggested prefetches exceed L2 MSHR queue.

\item \textbf{Enhanced Filter}\newline Original SPP introduces a
  concept of Prefetch Filter, which keeps a track of up to 1024 L2
  Cache prefetches suggested by SPP.  The Filter was modified to store
  meta-data like program counter, memory access address etc.  This is
  needed to train the perceptron when the result of that particular
  prefetch gets available.  At training time, this data is used to
  retrieve the state of the prefetcher when the prediction was made.

@@

\subsection{The Perceptron Layer}
As discussed earlier, the perceptron layer was introduced to act as a
throttler to the underlying SPP engine.  This section explores the
details of the perceptron layer and the range of features that are
ultimately used by the perceptron for correlating the prefetches.

The neural network weights are stored in separate tables for each
feature.  The indexing of each feature is done using different number
of bits.  At most 12 bits of a feature are used to index into the
perceptron table.  Certain features require more resolution power
\textit{i.e.}, full 12 bits of indexing.  On the other hand, some
features requiring lower resolution required as low as 7 bits of
indexing.  The variable indexing was determined by studying the
features and fine-tuned empirically so as to achieve a good accuracy
vs area trade-off.  Exact details are mentioned under `Area Overheads'
in Section XX.

@@

When SPP gets triggered, it suggests up to 4 (=Associativity of the
Pattern Table) candidates for prefetch based on the demand access
address.  In each subsequent lookahead depth, SPP suggests up to 4
more prefetch candidates, as explained in section\_\_.  All these
recommended prefetches are tested in the perceptron throttler before
they can access the Prefetch Filter, as in the original SPP data-path.

@@

Once all the weights are retrieved, they are added together, much like
the traditional perceptron dot product.  On obtaining the overall sum,
it is thresholded based on the preset threshold PERC\_THRESHOLD\_LO.
Only the prefetch candidates with the perceptron sum higher that the
threshold qualify for prefetching.  The prefetches that qualify the
perceptron throttler stage go through the Prefetch Filter stage, just
as in the SPP design.  The Prefetch Filter eliminates any redundant
prefetch suggestions.  In SPP-Perc, all the meta-data that is required
to recreate the features is also stored in the Prefetch Filter.  At a
later stage, when the feedback of the current prefetched line is
available, the stored data can be used to train the perceptron.

@@

In addition to the Prefetch Filter mentioned above, SPP-Perc also
maintains a `Reject Filter'.  Reject filter is a 1024-entry deep 1-way
associative table.  In case that a prefetch suggestion is rejected by
perceptron throttler, it instead gets logged into the Reject Filter.
The Reject Filter keeps track of 1024 entries that were suggested by
the Pattern Table but got rejected by the perceptron throttler.  This
can be used to train the perceptron to avoid false negatives
\textit{i.e.}, cases where prediction was to reject the prefetch but
the prefetch would have been useful.

As previously stated, an enhancement to the original SPP design
includes storing all the meta-data describing the program state at the
instant of prefetching, in the Prefetch Filter.  This information is
useful when the perceptron needs to be updated subsequently.

\textbf{TRAINING}\newline In the prefetching environment, feedback of
a prefetch is received whenever there is an eviction or a demand
access from L2 Cache.  This acts as a trigger to update all the
baseline SPP entries and to also train the perceptron throttler.
Training of the perceptron throttler involves restoring the meta-data
that was stored in Prefetch Filter or the Reject Filter.  This is done
by indexing into the corresponding filters using the cache line
address of the block being used to train. (10-bits indexing + 6-bits
tag matching).  Once the state of the program at the time of
prefetching is available, it is used to index into the perceptron
weights table.

@@

A secondary training mechanism also kicks in during demand fetches.
Before the demand access triggers the next set of prefetches, it
checks the Reject Filter for the valid entry.  In case it is a hit,
that means that the corresponding cache line was initially suggested
by the underlying SPP engine but rejected by the perceptron throttler.
This means that perceptron should have been more confident about that
particular prefetch.  Once such a scenario is identified, the state of
the execution at the time of prefetch is retrieved from the Reject
Table.  The retrieved data is used to index into the various weights
tables of the perceptron and the corresponding values are updated by
+1, saturating between and -16 and +15.  This update reflects
increased confidence for the prediction corresponding to that
prefetch.

This mechanism allows us to solve the classical problem of exploiting
`lost opportunity'.  In prior perceptron based implementations (and in
general, prefetching algorithms), there is usually no way of knowing
the result of not prefetch a particular line.  Our two-step SPP-Perc
allows us to overcome that issue in a simple manner.

\subsection{Features used by Perceptron}

Here we discuss the various features which help correlate the
prefetching decision with the program behaviour
\begin{itemize}
\item \textbf{Base address} of the demand access which triggered the
  prefetch.  Since prefetch are triggered from the L2 demand access,
  they tend to be correlated with the triggering address.

\item \textbf{Cache line} and \textbf{Page address}: These two
  separate features are derived from the base address which triggered
  the prefetch, as follows: base\_addr >> LOG2\_BLOCK \_SIZE and
  base\_addr >> LOG2\_PAGE\_ SIZE respectively.  The idea behind using
  three different shifted versions of the same feature is that it
  allows us to look into a wider range of bits than with a single
  version.  It also helps give more importance to the overlapping bits
  and lesser importance to most and least significance bits.  This
  approach can also eliminate destructive interference that can be
  caused by directly folding the bits into half.

@@

\item \textbf{Program Counter XOR Depth}: PC is for the instruction
  which triggered the prefetch chain.  Depth refers to the iteration
  count of the lookahead stages.  In general, PC is not considered as
  a good basis for doing lookahead prefetching as all the prefetches
  with depth >= 1 gets aliased onto the same PC which won't be true in
  actual demand fetch case.  This feature resolves a PC into a
  different value for each lookahead depth of SPP speculation, giving
  a more accurate correlation in lookahead cases.  This is akin to the
  concept of Virtual Program Counters\cite{VPC} introduced by Kim
  \textit{et. al.} for indirect branch prediction.

\item \textbf{PC\textsubscript{1} XOR PC\textsubscript{2}>>1 XOR
    PC\textsubscript{3}>>2}: Here $PC_i$ refers to the last $i^{th}$
  PC before the instruction that triggered the current prefetch.
  Hashing together the last three PCs tell SPP-Perc about the path
  that led to the current demand access and helps capture and
  branching information of the current basic block.  PCs are shifted
  in the increasing order of history before being hashed together.
  This is done to avoid the resultant value of zero in case 2 or more
  PCs are the same.  Additionally, obfuscating the information as it
  gets old allows us to get a wider and an approximate look into the
  program history.

\item \textbf{Current Signature XOR Delta}: It can be recalled from
  the discussion of SPP in section XX that the new signature is
  generated using the old signature and the blobk delta.  While
  `Current Signature XOR Delta' is not the exact formula for
  generating the future signature, it gives an approximate idea of the
  path that the combination of these two values can lead to.

@@

Some of the composite features are derive from simple hashing (XOR) of
two primary features.  There is always a question of usefulness of
such composite features and the `fresh' information added.  We try to
justify the choice of each feature by quantifying the contribution
made towards predicting prefetch behaviour, in Section XX.  Finally,
as noted above, each feature indexes into its independent entry of
perceptron weights.

>>>>

\section{NATCH Architecture}
\label{Design}

In this section we describe our implementation of NATCH.
NATCH is a generalised prefetch throttler and can be adapted to 
any existing or upcoming prefetcher with minimal modifications.
For a practical implementation, we have used SPP as the base engine prefetcher.

\subsection{Changes made to original SPP}
\label{Design-Changes}
To modify the SPP design to suit our scheme, the following changes were made:

\begin{itemize}
\item \textbf{Original Thresholds discarded}\newline In the original
  SPP design, the internal confidence was
  compared against a preset PF\_THRESHOLD (T\textsubscript{p}) to
  decide whether to accept or reject the prefetch suggestion.
  Furthermore, the accepted suggestions were thresholded against FILL
  \_THRESHOLD (T\textsubscript{f}) to decide the fill level: L2 Cache
  vs Last Level Cache.  T\textsubscript{p} and T\textsubscript{f} were
  set to 25 and 90 respectively, on the scale of 0 to 100.  In
  NATCH, the perceptron sum is used to make these decisions.  Hence
  these two thresholds are no longer needed

%%[NOTE] Can this point be removed?
\item \textbf{Looking at L2 MSHR Queue while prefetching}\newline
  Original SPP would not consider the slots available in the L2 MSHR
  queue.  It had an assumption that at no time can the number of
  prefetches suggested by SPP could exceed the capacity of the queue.
  While it was not proven in the paper, the internal confidence
  mechanism along with the thresholds made sure that the above
  assumption was maintained.  In NATCH since there can be no
  assumption on the degree of aggressiveness of the underlying prefetcher, 
  we explicitly check that at no point
  should the number of suggested prefetches exceed L2 MSHR queue.

\item \textbf{Enhanced Filter}\newline Original SPP introduces a
  concept of Prefetch Filter, which keeps a track of up to 1024 L2
  Cache prefetches suggestions.  For NATCH, the Filter was modified to store
  meta-data like program counter, memory access address etc.  This is
  needed to train the perceptron when the result of that particular
  prefetch gets available.  At training time, this data is used to
  retrieve the state of the prefetcher when the prediction was made.

@@

\subsection{The Perceptron Layer}
\label{Design-Perceptron}
As discussed earlier, the perceptron layer was introduced to act as a
throttler to the underlying prefetchh engine.  This section explores the
details of the perceptron layer and the range of features that are
ultimately used by the perceptron for correlating the prefetches.

The neural network weights are stored in separate tables for each
feature.  The indexing of each feature is done using different number
of bits.  At most 12 bits of a feature are used to index into the
perceptron table.  Certain features require more resolution power
\textit{i.e.}, full 12 bits of indexing.  On the other hand, some
features requiring lower resolution required as low as 7 bits of
indexing.  The variable indexing was determined by studying the
features and fine-tuned empirically so as to achieve a good accuracy
vs area trade-off.  Exact details are mentioned under `Area Overheads'
in Section \ref{Method-Overheads}

@@

When the base prefetcher gets triggered, it starts suggesting candidates for prefetching. 
All these
recommended prefetches are tested in the perceptron throttler before
they can access the Prefetch Filter, as in the original SPP data-path.

@@

Once all the weights are retrieved, they are added together, much like
the traditional perceptron dot product.  On obtaining the overall sum,
it is thresholded based on the preset threshold PERC\_THRESHOLD\_LO.
Only the prefetch candidates with the perceptron sum higher that the
threshold qualify for prefetching.  The prefetches that qualify the
perceptron throttler stage go through the Prefetch Filter stage.  
The Prefetch Filter eliminates any redundant
prefetch suggestions.  In NATCH, all the meta-data that is required
to recreate the features is also stored in the Prefetch Filter.  At a
later stage, when the feedback of the current prefetched line is
available, the stored data can be used to train the perceptron.

@@

In addition to the Prefetch Filter mentioned above, NATCH also
maintains a `Reject Filter'.  Reject filter is a 1024-entry deep 1-way
associative table.  In case that a prefetch suggestion is rejected by
perceptron throttler, it instead gets logged into the Reject Filter.
The Reject Filter keeps track of 1024 entries that were suggested by
the Pattern Table but got rejected by the perceptron throttler.  This
can be used to train the perceptron to avoid false negatives
\textit{i.e.}, cases where prediction was to reject the prefetch but
the prefetch would have been useful.

As previously stated all the meta-data describing the program state at the
instant of prefetching, is stored in the Prefetch Filter or the Reject Filter.  
This information is useful when the perceptron needs to be updated subsequently.

\textbf{TRAINING}\newline In the prefetching environment, feedback of
a prefetch is received whenever there is an eviction or a demand
access from L2 Cache.  This acts as a trigger to update all the
base prefetcher entries and to also train the perceptron throttler.
Training of the perceptron throttler involves restoring the meta-data
that was stored in Prefetch Filter or the Reject Filter.  This is done
by indexing into the corresponding filters using the cache line
address of the block being used to train. (10-bits indexing + 6-bits
tag matching).  Once the state of the program at the time of
prefetching is available, it is used to index into the perceptron
weights table.

@@

A secondary training mechanism also kicks in during demand fetches.
Before the demand access triggers the next set of prefetches, it
checks the Reject Filter for the valid entry.  In case it is a hit,
that means that the corresponding cache line was initially suggested
by the underlying prefetch engine but rejected by the perceptron throttler.
This means that perceptron should have been more confident about that
particular prefetch.  Once such a scenario is identified, the state of
the execution at the time of prefetch is retrieved from the Reject
Table.  The retrieved data is used to index into the various weights
tables of the perceptron and the corresponding values are updated by
+1, saturating between and -16 and +15.  This update reflects
increased confidence for the prediction corresponding to that
prefetch.

This mechanism allows us to solve the classical problem of exploiting
`lost opportunity'.  In prior perceptron based implementations (and in
general, prefetching algorithms), there is usually no way of knowing
the result of not prefetch a particular line.  Our two-step NATCH
architecture allows us to overcome that issue in a simple manner.

\subsection{Features used by Perceptron}
\label{Design-Features}
Here we discuss the various features which help correlate the
prefetching decision with the program behaviour
\begin{itemize}
\item \textbf{Base Address} of the demand access which triggered the
  prefetch.  Since prefetch are triggered from the L2 demand access,
  they tend to be correlated with the triggering address.

\item \textbf{Cache Line} and \textbf{Page Address}: These two
  separate features are derived from the base address which triggered
  the prefetch, as follows: base\_addr >> LOG2\_BLOCK \_SIZE and
  base\_addr >> LOG2\_PAGE\_ SIZE respectively.  The idea behind using
  three different shifted versions of the same feature is that it
  allows us to look into a wider range of bits than with a single
  version.  It also helps give more importance to the overlapping bits
  and lesser importance to most and least significance bits.  This
  approach can also eliminate destructive interference that can be
  caused by directly folding the bits into half.

\item \textbf{Program Counter XOR Depth}: PC is for the instruction
  which triggered the prefetch chain.  Depth refers to the iteration
  count of the lookahead stages.  In general, PC is not considered as
  a good basis for doing lookahead prefetching as all the prefetches
  with depth >= 1 gets aliased onto the same PC which won't be true in
  actual demand fetch case.  This feature resolves a PC into a
  different value for each lookahead depth of prefetch speculation, giving
  a more accurate correlation in lookahead cases.  This is akin to the
  concept of Virtual Program Counters\cite{VPC} introduced by Kim
  \textit{et. al.} for indirect branch prediction.

\item \textbf{PC\textsubscript{1} XOR PC\textsubscript{2}>>1 XOR
    PC\textsubscript{3}>>2}: Here $PC_i$ refers to the last $i^{th}$
  PC before the instruction that triggered the current prefetch.
  Hashing together the last three PCs tell NATCH about the path
  that led to the current demand access and helps capture and
  branching information of the current basic block.  PCs are shifted
  in the increasing order of history before being hashed together.
  This is done to avoid the resultant value of zero in case 2 or more
  PCs are the same.  Additionally, obfuscating the information as it
  gets old allows us to get a wider and an approximate look into the
  program history.

@@

\item \textbf{Current Signature XOR Delta}: It can be recalled from
  the discussion of SPP in Section \ref{Background-SPP} that the new signature is
  generated using the old signature and the blobk delta.  While
  `Current Signature XOR Delta' is not the exact formula for
  generating the future signature, it gives an approximate idea of the
  path that the combination of these two values can lead to.

\item \textbf{Page Address XOR Confidence}: This feature helps look at the 
tendency of each page to be prefetch friendly or prefetch averse. It 
helps resolve a page into different entries depending on its confidence 
for prefetching, which can vary during phases of a program execution.

@@

Some of the composite features are derive from simple hashing (XOR) of
two primary features.  There is always a question of usefulness of
such composite features and the `fresh' information added.  We try to
justify the choice of each feature by quantifying the contribution
made towards predicting prefetch behaviour, in Section \ref{Method-Features}.  Finally,
as noted above, each feature indexes into its independent entry of
perceptron weights.

\subsection{Generalizing NATCH for any Prefetcher}
\label{Design-Generalizing}
The above implementation of NATCH suggests that it is highly modular and can be 
adapted to be used over any base prefecher for increased prefetch accuracy. 
In our implementation, 
only two `hooks' are required between NATCH and the baseline SPP. First  
is to make sure that all the prefetch candidates of SPP pass through 
the perceptron throttler and if qualified, the metadata for perceptron indexing
be stored. Second is needed when the feedback of a prior prefetch is available in form 
of a subsequent demand hit or cache eviction. In that case, the stored meta-data needs 
to be retrieved to update the state of the perceptrons.

In general, NATCH can be adapted to a new base prefetcher with only a few modifications.
\begin{itemize}

\item \textbf{Enhancing the Base Prefetcher:} By tuning down any internal thresholds 
to increase its inherent aggressiveness.

\item \textbf{Inferencing and Storing:} All prefetch recommendations to be tested 
using the perceptron inferencing algorithm.
Perceptron output: \textit{true} and \textit{false} should be saved appropriately, along with all 
the meta-data required for perceptron indexing.

\item \textbf{Retrieving and Training:} When the feedback is available, the previously 
stored meta-data can be used to re-index into the perceptron entries and increment / decrement 
the weights.

\item \textbf{Feature Selection:} Six out of the nine features we developed use information derived 
from program execution, irrespective of the baseline SPP prefetcher. Beyond that, the feature set 
can be expanded to convey any useful information from the prefetcher to the perceptron throttler.
For example, in our implementation 'Confidence', 'Current Signature XOR Delta', and 
'Page Address XOR Confidence' are such features.

### 2018-11-16 intro.tex
Incorporating suggestions

\section{Introduction}
Since past few decades, processor and memory scaling has been enabled
with different philosophies in mind.  While processor scaling focused
on speed improvements, memory scaling was centred around increasing
the storage capacity.  The process technology reaching scaling
limitations led to Memory Wall\cite{MemWall} - the increasing
performance gap between the processor speed and the memory speeds.
Various techniques have been developed to combat this widening gap.
Data prefetching is one such important technique.  Data prefetching
exploits the fact that in most applications, memory accesses have a
well-defined pattern.

@@

To this effect we propose SPP-Perc <come up with a catchy name>.  It
is an enhancement to the existing state of the art prefetcher and
overcomes the coverage vs accuracy trade-off in a robust manner.  The
idea is to modify SPP design to make it as aggressive as it can get.
This enables SPP to capture complex memory access patterns hence
leading to increased coverage.  This comes at a cost of increased DRAM
traffic, hence reduction in overall IPC.  The prefetch suggestions
recommended by SPP pass through the perceptron based throttler.  Over
time, perceptron layer learns to correlate the prefetches recommended
by SPP with various available features, leading to elimination of
useless prefetches.  This leads to an overall increased accuracy of
the prefetch scheme and reduction in DRAM traffic.

\vspace{1ex}This paper talks about SPP-Perc, its merits, analysis and
future scope for expansion.  The contributions made by this paper are:

@@

\item Examining the perceptron weights doing a statistical study to
  quantify the contribution made by each feature.  We have also used
  this idea to develop a comprehensive set of features where each
  feature contributes some `new' information to the perceptron.  The
  details are explained under methodology, in Section XX.

\item Cross-validating the design across benchmarks.  All the
  development and parameter tuning was done on the SPEC 2017
  benchmark.  The results have been shown to be consistent across
  unseen benchmarks.  More details can be found in the results section
  (Section XX).

  % \item Designing the prefetcher keeping SPEC 2017 benchmark suite
  %   in mind.  We have used SPEC 2017 to compare SPP-Perc against the
  %   highest performing prefetchers.  We have also used our
  %   prefetcher to characterize memory intensive benchmarks of the
  %   SPEC 2017 suite, with respect to prefetching.

  % \item We came up with an efficient model to use the perceptron
  %   output as a representation of the prefetch confidence using an
  %   on-line histogram technique.  We show how the simple sum can
  %   replace the existing mechanism which was essentially based on
  %   counting the number of hits for a particular entry in SPP.

@@

We tested SPP-Perc on Champsim, an open source simulator which models
an Out-of-Order CPU using.  For evaluation, we used SPEC 2017
benchmarks.  On a single core configuration, SPP-Perc increases
performance of the system by 39.5\% as compared to the baseline with
no prefetching, on the memory intensive subset of the benchmark.  This
outperforms the next best prefetcher, SPP, by 6.84\%.  On a multi-core
system running a mix of memory intensive subset of the SPEC 2017
traces, SPP-Perc saw an improvement of 11.9\% over SPP for 4-core
system and 10.67\% for 8-core system.

In the results part in section XX, we show a detailed analysis of the
speedup achieved.  We also used SPEC 2006 and CloudSuite benchmarks
for cross-validation of the prefetcher implementation.

The rest of the paper is organized as follows.  Section 2 talks about
background work and recaptures the SPP architecture Section 3
discusses the detailed implementation of the perceptron mechanism and
the features used.  Section 4 consists of the evaluation methodology
and explores the feature space for perceptron learning.  Section 5 is
the performance evaluation of our prefetcher and Section 6 concludes
the paper.

>>>>

\section{INTRODUCTION}
\label{Introduction}
Since past few decades, processor and memory scaling has been enabled
with different philosophies in mind.  While processor scaling focused
on speed improvements, memory scaling was centred around increasing
the storage capacity.  The process technology reaching scaling
limitations led to Memory Wall\cite{MemWall} - the increasing
performance gap between the processor speed and the memory speeds.
Various techniques have been developed to combat this widening gap.
Data prefetching is one such important technique.  Data prefetching
exploits the fact that in most applications, memory accesses have a
well-defined pattern.

@@

To this effect we propose NATCH: NeurAl prefeTCh tHrottler.  It
is an enhancement to the existing state of the art prefetcher and
overcomes the coverage vs accuracy trade-off in a robust manner.  The
idea is to use a state-of-the-art prefetcher as the base engine.
For that we choose Signature Path Prefetcher (SPP) and 
modify the design to make it as aggressive as it can get.
This enables the base engine to capture complex memory access patterns hence
leading to increased coverage.  This comes at a cost of increased DRAM
traffic, hence reduction in overall IPC.  The prefetch suggestions
recommended by SPP pass through the perceptron based throttler. Over
time, perceptron layer learns to correlate the prefetch recommendations 
with various available features, leading to elimination of
useless prefetches. This leads to an overall increased accuracy of
the prefetch scheme and reduction in DRAM traffic.

\vspace{1ex}This paper talks about NATCH, its merits, analysis and
future scope for expansion.  The contributions made by this paper are:

@@

\item Examining the perceptron weights doing a statistical study to
  quantify the contribution made by each feature.  We have also used
  this idea to develop a comprehensive set of features where each
  feature contributes some `new' information to the perceptron.  The
  details are explained under methodology, in Section \ref{Method-Overheads}.

\item Cross-validating the design across benchmarks.  All the
  development and parameter tuning was done on the SPEC 2017
  benchmark.  The results have been shown to be consistent across
  unseen benchmarks.  More details can be found in Section \ref{Results-CrossVal}.

@@

We tested NATCG on Champsim, an open source simulator which models
an Out-of-Order CPU using.  For evaluation, we used SPEC 2017
benchmarks.  On a single core configuration, NATCH increases
performance of the system by 39.5\% as compared to the baseline with
no prefetching, on the memory intensive subset of the benchmark.  This
outperforms the next best prefetcher, SPP, by 6.84\%.  On a multi-core
system running a mix of memory intensive subset of the SPEC 2017
traces, NATCH saw an improvement of 11.9\% over SPP for 4-core
system and 10.67\% for 8-core system.

In the results part in Section \ref{Results}, we show a detailed analysis of the
speedup achieved.  We also used SPEC 2006 and CloudSuite benchmarks
for cross-validation of the prefetcher implementation.

The rest of the paper is organized as follows.  Section \ref{Background} talks about
background work and recaptures the SPP architecture Section \ref{Design}
discusses the detailed implementation of the perceptron mechanism and
the features used.  Section \ref{Method} consists of the evaluation methodology
and explores the feature space for perceptron learning.  Section \ref{Results} is
the performance evaluation of our prefetcher and Section \ref{Conclusion} concludes
the paper.
